Token-level author diarization using clustering of stylistic contexts

### 2017-06-03 paper/paper.tex
no comment

\citet{rosso-2016} divided the PAN 2016 author diarization task into three subtasks. The first subtask is traditionally called intrinsic plagiarism detection (IPD). The goal of this task is to find plagiarized parts of a document in which at least $70\%$ of text is written by main author and the rest by one or more other authors. The term \emph{intrinsic} means that a decision whether a part of the document is plagiarized has to be made only by analysing the given document, without any comparisons with external sources. In the rest of the paper we refer to this subtask as Task \emph{a}.

@@

\paragraph{Clustering.}
The final step in our approach is clustering of obtained feature vectors which represent stylistic contexts of tokens. The number of clusters is equal to the number of authors in tasks \emph{a} and \emph{b}, but in Task \emph{c} it is unknown. We tested various clustering algorithms available in scikit-learn\footnote{\url{http://scikit-learn.org}} Python toolkit by \citet{scikit-learn} in all tasks. In Model A for tasks  \emph{a} and \emph{b} we propose hierarchical agglomerative clustering, and for Task \emph{c} DBSCAN algorithm which estimates the number of clusters automatically. In Model B we use k-means for clustering in all tasks, and tried predicting the number of clusters based on the elbow rule. This is described in more detail in section \ref{sec:experimental-results}

@@

For clustering algorithm selection we used manual search over several algorithms. We split the whole dataset into a training and a test set. For each algorithm we were examining, a grid search of its hyperparameters was performed on the training set. We selected an algorithm and hyperparameters that achieved the best performance on the training set (since this is an unsupervised approach), and reported the final performance on the test set.

In Task \emph{a}, we used $50\%$ of the dataset as a training set, and the other half as a test set. Since this task is characterized as an outlier detection task, we tested an isolation forest algorithm, but achieved poor results. Other algorithms which we evaluated were Gaussian mixtures and hierarchical agglomerative clustering. Cosine affinity and average linkage with agglomerative clustering achieved the best macro $F_1$ (described in subsection \ref{subsec:evaluation-measures}) performance on the training set and we report its result on the test set.

For Task \emph{b} we split the dataset in two halves as well. Grid search for the best hyperparameters was performed for agglomerative clustering. The best performance on the training set was obtained with euclidean affinity and average linkage. For Task \emph{c} we should have somehow determined the number of clusters. Due to a lack of time we decided to test algorithms which can determine this number automatically, i.e. this is not a hyperparameter which should be known in advance. Since we noticed that grid searches take a lot of time, we reduced a training set from $50\%$ to $10\%$ and repeated all experiments. We tested DBSCAN, affinity propagation, and mean shift algorithms.

@@

Since the model with the best achieved Bcubed $F_1$-score ($0.61$) is not of practical use in real life applications because the number of clusters is always wrongly estimated, we decided to repeat the grid search in Task \emph{c} for DBSCAN, but this time we used the Calinski-Harabaz index defined by \citet{calinski-1974} as evaluation measure since it does not require the real number of clusters for clustering evaluation. Finally, from all results on training set we chose (\texttt{eps=0.23, min\_samples=64, metric="cosine"}) for the final hyperparameters. This wasn't the best combination, but it produced relatively acceptable amount of noisy elements per document, and performed quite fast but again didn't estimate the correct number of clusters in most cases. If some samples weren't clustered, we assigned them the majority label from neighborhood (context) of size $10$ ($5$ on each side), or the majority label from all samples if samples in the context weren't clustered.

>>>>

\citet{rosso-2016} divided the PAN 2016 author diarization task into three subtasks. The first subtask is traditionally called intrinsic plagiarism detection (IPD). The goal of this task is to find plagiarized parts of a document in which at least $70\%$ of text is written by main author and the rest by one or more other authors. The term \emph{intrinsic} means that a decision whether a part of the document is plagiarized has to be made only by analysing the given document, without any comparisons with external sources. This was our main motivation for solving this and other subtasks. In the rest of the paper we refer to this subtask as Task \emph{a}.

@@

\paragraph{Clustering.}
The final step in our approach is clustering of obtained feature vectors which represent stylistic contexts of tokens. The number of clusters is equal to the number of authors in tasks \emph{a} and \emph{b}, but in Task \emph{c} it is unknown. We tested several clustering algorithms available in scikit-learn\footnote{\url{http://scikit-learn.org}} Python toolkit by \citet{scikit-learn} in all tasks. In Model A for tasks  \emph{a} and \emph{b} we propose hierarchical agglomerative clustering, and for Task \emph{c} DBSCAN algorithm which estimates the number of clusters automatically. In Model B we use k-means for clustering in all tasks, and tried predicting the number of clusters based on the elbow rule. This is described in more detail in section \ref{sec:experimental-results}

@@

For clustering algorithm selection we used manual search over several algorithms. We split the whole dataset into a training and a test set. For each algorithm we were examining, a grid search of its hyperparameters was performed on the training set. We selected an algorithm and hyperparameters that achieved the best performance on the training set (since this is an unsupervised approach), and reported the final performance on the test set. We didn't include the k-means algorithm in clustering model selection since we used it for context size estimation.

In Task \emph{a}, we used $50\%$ of the dataset as a training set, and the other half as a test set. Since this task is characterized as an outlier detection task, we tested an isolation forest algorithm, but achieved poor results. Other algorithm which we evaluated was hierarchical agglomerative clustering which achieved the best macro $F_1$ (described in subsection \ref{subsec:evaluation-measures}) with cosine affinity and average linkage on the train set. We report its result on the test set.

For Task \emph{b} we split the dataset in two halves as well. Grid search for the best hyperparameters was performed for agglomerative clustering. The best performance on the training set was obtained with euclidean affinity and average linkage. For Task \emph{c} we should have somehow determined the number of clusters. Due to a lack of time we decided to test algorithms which can determine this number automatically, i.e. this is not a hyperparameter which should be known in advance. Since we noticed that grid searches take a lot of time, we reduced a training set from $50\%$ to $10\%$ and repeated all experiments. We tested DBSCAN and affinity propagation algorithms.

@@

Since the model with the best achieved Bcubed $F_1$-score ($0.61$) is not of practical use in real life applications because the number of clusters is always wrongly estimated, we decided to repeat the grid search in Task \emph{c} for DBSCAN, but this time we used the Calinski-Harabaz index defined by \citet{calinski-1974} as evaluation measure since it does not require the real number of clusters for clustering evaluation. Finally, from all results on training set we chose (\texttt{eps=0.23, min\_samples=64, metric="cosine"}) for the final hyperparameters. This wasn't the best combination, but it produced relatively acceptable amount of noisy (non-clustered) elements per document, and performed quite fast but again didn't estimate the correct number of clusters in most cases. If some samples weren't clustered, we assigned them the majority label from neighborhood (context) of size $10$ ($5$ on each side), or the majority label from all samples if samples in the context weren't clustered.
